Computationally Efficient Simulation of Queues: The \proglang{R} Package \pkg{queuecomputer}

### 2020-07-18 paper.tex
Added section 4. output from code.

The purpose of the package \pkg{queuecomputer} is to compute, deterministically, the output of a queueing system given the arrival and service times for all customers. The most important function is \code{queue\_step}. The first argument to  \code{queue\_step} is a vector of arrival times, the second argument is a vector of service times and the third argument specifies the servers available. 
%
\begin{CodeChunk}
\begin{Sinput}
R> library("queuecomputer")
R> arrivals <- cumsum(rexp(100))
R> head(arrivals)
\end{Sinput}
\begin{Soutput}
[1] 0.693512 1.693399 2.425550 3.952405 3.961906 4.405492
\end{Soutput}
\begin{Sinput}
R> service <- rexp(100)
R> departures <- queue_step(arrivals, service = service, servers = 2)
R> departures
\end{Sinput}
\begin{Soutput}
# A tibble: 100 x 6
   arrivals     service departures      waiting system_time server
      <dbl>       <dbl>      <dbl>        <dbl>       <dbl>  <dbl>
1  0.693512 0.830158956   1.523671 0.000000e+00 0.830158956      1
2  1.693399 0.817648174   2.511047 1.110223e-16 0.817648174      2
3  2.425550 0.002675641   2.428226 2.138047e-16 0.002675641      1
4  3.952405 0.667180991   4.619586 4.440892e-16 0.667180991      1
5  3.961906 0.551920432   4.513827 4.440892e-16 0.551920432      2
6  4.405492 1.069236762   5.583063 1.083341e-01 1.177570886      2
7  4.594253 1.110448926   5.730035 2.533279e-02 1.135781711      1
8  4.993053 0.766944956   6.350008 5.900099e-01 1.356954853      2
9  6.047412 0.805061421   6.852474 1.110223e-16 0.805061421      1
10 6.856338 1.317802131   8.174140 0.000000e+00 1.317802131      2
# ... with 90 more rows
\end{Soutput}
\end{CodeChunk}
%
The output of a \code{queue\_step} function is a `\code{queue\_list}'
object. We built a \code{summary} method for objects of class
`\code{queue\_list}', which we now demonstrate.
%
\begin{CodeChunk}
\begin{Sinput}
R> summary(departures)
\end{Sinput}
\begin{Soutput}
Total customers:
 100
Missed customers:
 0
Mean waiting time:
 0.246
Mean response time:
 1.11
Utilization factor:
 0.53
Mean queue length:
 0.301
Mean number of customers in system:
 1.36
\end{Soutput}
\end{CodeChunk}
%
If the last element of $\mathbf{y}$ is zero, it is possible that some
customers will never be served, this is the ``Missed customers''
output. The performance measures that follow are the mean waiting time
$\bar{w}$, the mean response time $\bar{r} = d - a$, the observed
utilization factor $\bar{B}/K$, the mean queue length and the mean
number of customers in the system respectively. The utilization factor
$\bar{B}/K$ takes into account the changing number of open servers
$K(t)$ where Algorithm~\ref{alg:changing_servers} is used. We now
explain the implementation details of the package.

>>>>

The purpose of the package \pkg{queuecomputer} is to compute, deterministically, the output of a queueing system given the arrival and service times for all customers. The most important function is \code{queue\_step}. The first argument to  \code{queue\_step} is a vector of arrival times, the second argument is a vector of service times and the third argument specifies the servers available. 
%
\begin{CodeChunk}
\begin{Sinput}
R> library("queuecomputer")
R> arrivals <- cumsum(rexp(100))
R> head(arrivals)
\end{Sinput}
\begin{Soutput}
[1] 0.7551818 1.9368246 2.0825313 2.2223266 2.6583952 5.5533638
\end{Soutput}
\begin{Sinput}
R> service <- rexp(100)
R> departures <- queue_step(arrivals, service = service, servers = 2)
R> departures
\end{Sinput}
\begin{Soutput}
# A tibble: 100 x 6
arrivals service departures   waiting system_time server
<dbl>   <dbl>      <dbl>     <dbl>       <dbl>  <int>
1    0.755   1.90        2.66 -2.22e-16       1.90       1
2    1.94    0.516       2.45  0.             0.516      2
3    2.08    0.449       2.90  3.70e- 1       0.819      2
4    2.22    0.380       3.03  4.33e- 1       0.812      1
5    2.66    1.25        4.15  2.44e- 1       1.49       2
6    5.55    2.69        8.25  4.44e-16       2.69       1
7    6.78    0.196       6.98 -2.50e-16       0.196      2
8    7.32    2.30        9.62  0.             2.30       2
9    8.28    0.566       8.84  0.             0.566      1
10    8.43    0.763       9.61  4.19e- 1       1.18       1
# … with 90 more rows
\end{Soutput}
\end{CodeChunk}
%
The output of a \code{queue\_step} function is a `\code{queue\_list}'
object. We built a \code{summary} method for objects of class
`\code{queue\_list}', which we now demonstrate.
%
\begin{CodeChunk}
\begin{Sinput}
R> summary(departures)
\end{Sinput}
\begin{Soutput}
Total customers:
100
Missed customers:
0
Mean waiting time:
0.18
Mean response time:
1.15
Utilization factor:
0.466341252182172
Mean queue length:
0.174
Mean number of customers in system:
1.11
\end{Soutput}
\end{CodeChunk}
%
If the last element of $\mathbf{y}$ is zero, it is possible that some
customers will never be served, this is the ``Missed customers''
output. The performance measures that follow are the mean waiting time
$\bar{w}$, the mean response time $\bar{r} = d - a$, the observed
utilization factor $\bar{B}/K$, the mean queue length and the mean
number of customers in the system respectively. The utilization factor
$\bar{B}/K$ takes into account the changing number of open servers
$K(t)$ where Algorithm~\ref{alg:changing_servers} is used. We now
explain the implementation details of the package.
